\documentclass{ut-thesis}

\input{preamble}
% author data
\author{Tom Ginsberg}
\title{Identifying and Characterizing High Dimensional Covariate Shift with Learning Models}
\degree{Master of Science}
\department[]{Department of Computer Science}
\gradyear{2023}

\makeatletter
\renewcommand{\@makechapterhead}[1]{%
        {\noindent\raggedright\normalfont% Alignment and font reset
    \huge\bfseries \@chapapp\space\thechapter~~#1\par\nobreak}% Formatting
    \vspace{\baselineskip}% ...just a little space
}
\makeatother

% Document
\begin{document}
    \maketitle
    \begin{abstract}
        The ability to quickly and accurately identify covariate shift at test time is a critical and often overlooked component of safe machine learning systems deployed in high-risk domains.
        While methods exist for detecting when predictions should not be made on out-of-distribution test examples, identifying distributional level differences between training and test time can help determine when a model should be removed from the deployment setting and retrained.
        In this thesis, we explore modern and foundational methods for identifying and characterizing distributional shift in high dimensional data, in particular where such data is treated as the covariates to a learning model --- this type of distribution shift is known formally as covariate shift.
        We go on to provide a new definition for \textit{harmful covariate shift} ({\small HCS}) that goes beyond ideas from standard learning theory to give a richer insight on when covariate shift may hurt the performance of classification models.
        Motivated from our definition, we propose a method, the Detectron, to detect {\small HCS} based on the discordance between an ensemble of \textit{constrained disagreement classifiers} (CDCs)  trained to agree on training data and disagree on test data.
        We derive a loss function for training CDCs and show that their disagreement rate and predictive entropy represent powerful discriminative statistics for {\small HCS}.
%        Furthermore, we present tight finite sample shift detection guarantees in an idealized setting.
        Empirically, we demonstrate that the CDC learning algorithm produces model with behaviour that aligns well with our desideratum.
        Finally we showcase the ability of the Detectron to detect {\small HCS} with statistical certainty on a variety of high-dimensional datasets.
        Across numerous domains and modalities, we show state-of-the-art performance compared to existing methods, particularly when the number of observed test samples is small.
    \end{abstract}

    \begin{acknowledgements}
        I would first and foremost like to thank my graduate supervisor Professor Rahul G. Krishnan,
        for his continuous support and mentorship throughout my studies, as well as Professor Murat Erdogdu for
        his role as an additional reader for this thesis.
        I would also like to thank my original graduate cohort, Vahid Balazadeh, and Michael Cooper, for their
        help brainstorming ideas, useful feedback, research advice, squash playing and all
        around creation of an amazing lab environment.
        Additional thanks to others that provided helpful advice and feedback include:
        Edward De Brouwer, Aslesha Pokhrel, Zhongyuan Liang, Adnan Mohd, Ian Shi, Asic Chen and Stephan Rabanser.
    \end{acknowledgements}
    \tableofcontents
    \listoftables
    \listoffigures

    \chapter[Introduction]{Introduction: Covariate Shift}
    \label{ch:intro}

    \input{intro}


    \chapter[Background: Covariate Shift]{Background: Covariate Shift}\label{ch:related}

    \input{background}

    \chapter[Methodology: The Detectron]{Methodology: The Detectron}\label{ch:detectron}

    \input{detectron}


    \chapter{Applications and Experiments}\label{ch:experiments}
    \input{experiments}


    \chapter{Discussion}\label{ch:discussion}
    \input{discussion}


    \chapter{Conclusion, Limitations and Future Work}\label{ch:conclusion}
    \input{conclusion}

    \bibliography{bib}

    \appendix


    \chapter{Appendix}\label{ch:appendix}


    \section{Rejectron}\label{sec:rejectron}
    \input{rejectron}


    \section{Proofs}\label{sec:proofs}
    \input{proofs}

    \section{Constrained Disagreement Details}
    \label{sec:cons_dis_det}
    \input{constrained_dis.tex}

    \section{Experimental Details}
    \label{sec:expdet}
    \input{datasets_and_experimental_details}


\end{document}